\documentclass[a4paper,10pt]{article}

% --- PACKAGES ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel} % Se o curriculo for em PT-BR, mude para 'portuguese'
\usepackage{geometry}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{titlesec}
% For better line breaks in long URLs
\usepackage{xurl}

% --- DOCUMENT SETUP ---
% Set page margins to maximize content space
\geometry{top=1.0cm, bottom=1.0cm, left=1.0cm, right=1.0cm}

% Remove page numbers and headers for clean resume look
\pagestyle{empty}

% PDF metadata - IMPORTANT: Tell your friends to change this!
\hypersetup{
    pdftitle={CV Name Surname},
    pdfauthor={Name Surname},
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
    citecolor=black,
    bookmarksdepth=1 
}

% Disable section numbering for cleaner appearance
\setcounter{secnumdepth}{0}

% Format section headers with bold text and underline
\titleformat{\section}
{\Large\bfseries}
{}
{0em}
{}
[\titlerule\vspace{0.5ex}]

% --- BEGIN DOCUMENT ---
\begin{document}

% --- HEADER ---
\begin{center}
    {\LARGE \textbf{Your Full Name}} 
    \\ [0.1cm]
    City, State -- Country
    {\textbullet}
    +55 00 00000-0000
    \\ [0.1cm]
    Email: \href{mailto:email@example.com}{email@example.com} 
    {\textbullet}
    \href{https://www.linkedin.com/in/yourprofile/}{LinkedIn Profile} 
    {\textbullet}
    \href{https://github.com/yourusername}{GitHub Profile}
\end{center}

% --- SECTIONS ---

\section{Experience}
    % List work experience in reverse chronological order (most recent first)
    
    \subsection*{\texorpdfstring{
            \textbf{Company Name} \hfill [City, Country]
        }{
            Company Name -- Location
        }}
    \textit{Job Title \hfill Start Month Year -- End Month Year}
        \begin{itemize} 
            \item Describe your main responsibility or achievement here using action verbs.
            \item Example: Developed a new feature that reduced loading time by 30\%.
            \item Example: Collaborated with a team of X people to deliver project Y.
        \end{itemize}

    \subsection*{\texorpdfstring{
            \textbf{Previous Company Name} \hfill City, Country
        }{
            Previous Company -- Location
        }}
    \textit{Job Title \hfill Start Month Year -- End Month Year}
        \begin{itemize}
            \item Mention a specific tool or technology you used to solve a problem.
            \item Focus on results: "Improved process X by doing Y".
            \item Demonstrated soft skills like leadership, adaptability, or communication.
        \end{itemize}
        
% ------

\section{Projects} 
    % Include academic projects, freelance work, or personal portfolios
    
    \subsection*{\texorpdfstring{
            \textbf{Project Name} \hfill Context: e.g. Freelance / Final Project
        }{
            Project Name
        }}
    \textit{Your Role: e.g. Full Stack Developer}
        \begin{itemize}
            \item Briefly describe what the project is and what problem it solves.
            \item List the main technologies used (e.g. React, Node.js, SQL).
            \item Highlight a specific challenge you overcame during development.
        \end{itemize}

    \subsection*{\texorpdfstring{
            \textbf{Another Project Name} \hfill Context
        }{
            Another Project
        }}
    \textit{Your Role}
        \begin{itemize} 
            \item Description of the project functionalities.
            \item Outcome or impact of the project.
        \end{itemize}

% ------

\section{Skills}
    \begin{itemize}
        \item \textbf{Languages \& Frameworks:} List: e.g. Java, Python, C++, React, etc.
        \item \textbf{Databases:} List: e.g. MySQL, MongoDB, PostgreSQL
        \item \textbf{Tools:} List: e.g. Git, Docker, AWS, Azure, VS Code
        \item \textbf{Soft Skills:} List: e.g. Problem Solving, Team Leadership, Communication
        \item \textbf{Languages:} Native Language, Second Language (Level)
    \end{itemize}

% ------

\section{Education}
    % Use this format for each degree - most recent first
    \subsection*{\texorpdfstring{
            \textbf{University Name} \hfill City, Country
        }{
            University Name -- Location
        }}
    \textit{Degree Title, e.g. B.Sc. in Computer Science \hfill Start Date -- End Date or "Current"}

    \subsection*{\texorpdfstring{
            \textbf{Previous University or School} \hfill City, Country
        }{
            Previous School -- Location
        }}
    \textit{Degree or Certificate Title \hfill Start Date -- End Date}

\end{document}
